%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.3in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.00\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1.00\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.00\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
    
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize} \vspace{-18pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge \scshape Sheel Patel} \\ 
    \vspace{3pt}
    \small Brampton, ON $|$
    \vspace{3pt}
    \small s60patel@torontomu.ca $|$
    \vspace{3pt}
    \href{https://www.linkedin.com/in/s60patel/}
    {{LinkedIn}} $|$
    \href{https://github.com/Kyoko522/}{GitHub} $|$
    \href{https://sheelportfolio.vercel.app/}{Website}
    \vspace{-9pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Toronto Metropolitan University (formerly Ryerson University)}{Toronto, ON}
      {Bachelor of Science in Computer Science (Co-op); Dean's List}{Sep 2022 -- Present}
      \resumeItemListStart
        \resumeItem{\textit{Data Structures} (Algorithms, Java, C, Python (libraries: numpy, pytest, etc), Lisp, Elixir, Rust)}
        \resumeItem{\textit{Software Engineering I} (SDLC Models, Git, Agile Methods, Jira, MongoDB, Ruby, Go, DMBS)}
        \resumeItem{\textit{Operating Systems} (Distributed Systems, Multi-tiered, Embedded Systems), UNIX, and Linux (Bash, C, C++, VMs)}
        \resumeItem{\textit{Database(MySQL, MongoDB)}, Artificial Intelligence(Natural Language Understanding)}
        
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Full Stack Developer}{Sept 2023 -- Jun 2024}
      {Practical Applications of Computer Science (TMU Club)}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{\textbf{Developed} a websites with \textbf{React} and \textbf{PostgreSQL} which increased engagement among students to over 500 monthly views}
        \resumeItem{Led the development of an application with \textbf{Kotlin} and \textbf{Firebase} optimizing food usage impacting over \textbf{2000 students}.}
        \resumeItem{Coordinated TerraHack hackathon, managing end-to-end logistics for an event with over \textbf{1,000 applicants} and 250 selected participants, ensuring a seamless experience for all involved.}
        \resumeItem{Guided staff and volunteers, using \textbf{Jira} and \textbf{Conflunce} for timely task completion, enhancing workflow by 80\%.}

      \resumeItemListEnd
    \resumeSubheading
      {Lifeguard}{May 2023 -- Sept 2024}
      {Canada's Wonderland}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Supervised the safety of over 1000 patrons daily, reducing incident risks by 20\% through rigorous protocol enforcement.}
        \resumeItem{Completed more than 100 hours of advanced safety training, which enhanced my ability to solve problems quickly in high-stress scenarios.}
        \resumeItem{Managed over 30 successful rescues with precision, demonstrating capacity for calm and efficient crisis management.}
        \resumeItem{Engaged in seamless collaboration within the lifeguard team, cultivating essential coordination strategies that improved response times by 20\% during high-traffic beach days through effective shared protocols.}
        \resumeItem{Achieved a 100\% positive feedback rate from guests, showcasing adaptability and commitment to a customer-first approach.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \vspace{-3pt}
      
      \resumeProjectHeading
        {
        \textbf{\href{https://github.com/Kyoko522/Chess}{Java Chess Game}}
        }{\textbf{Java $|$ Java Swing $|$ Algorithm Design (Minimax, Alpha-Beta Pruning) $|$ Git}}
        \resumeItemListStart
            \resumeItem{Engineered a modular Java-based chess game using object-oriented principles, resulting in a clean and maintainable codebase.}
            \resumeItem{Developed an interactive chessboard interface with \textbf{Java Swing}, integrating smooth animations and intuitive UI elements.}
            \resumeItem{Implemented AI opponent logic with \textbf{Minimax} and \textbf{Alpha-Beta pruning}, demonstrating strong algorithmic skills.}
            \resumeItem{Integrated advanced chess mechanics such as pawn promotion, castling, and en passant.}
        \resumeItemListEnd
        \vspace{-7pt}
              
      \resumeProjectHeading
          {
          \textbf{\href{https://github.com/Kyoko522/EcoDex}{{AI Image Processing}}}
          }{\textbf{HTML $|$ CSS $|$ Next.js $|$ PostgreSQL $|$ OAuth}}
          \resumeItemListStart
            \resumeItem{Developed an AI-powered app for plant and insect identification with a retro-inspired UI using \textbf{React} and \textbf{Next.js}.}
            \resumeItem{Integrated \textbf{OpenAI API} for advanced image recognition, providing detailed insights into identified species.}
            \resumeItem{Implemented \textbf{OAuth} for secure, streamlined user authentication, enhancing data privacy and access control.}
            \resumeItem{Built camera and image upload via \textbf{HTML} and \textbf{Formik}, enabling real-time image capture, validation, and processing.}
            \resumeItem{Leveraged \textbf{Cloudinary} for efficient image storage and optimization, ensuring fast loading times and smooth user experience.}
          \resumeItemListEnd
          \vspace{-7pt}
          \resumeProjectHeading
        {
        \textbf{\href{https://github.com/Kyoko522/Dance-Club-Management-App}
        {Event Management System}}
        }{\textbf{Vue.js $|$ Azure $|$ Go $|$ Docker $|$ SQLite3 $|$ Git $|$ GitHub}}
        \resumeItemListStart
            \resumeItem{Developed a management system as to enhance operational efficiency in a simulated dance club environment.}
            \resumeItem{Built the front-end with \textbf{Vue.js}, improving scheduling and attendance tracking efficiency by 40\% compared to previous methods.}
            \resumeItem{Streamlined operations through process mapping and alternative solutions, using \textbf{Go} and         \textbf{SQLite3} for a robust back-end, ensuring data accuracy, compliance, and automated scheduling.}
            \resumeItem{Implemented \textbf{JWT} for secure authentication, demonstrating skills in dynamic access control and session management.}
          \resumeItemListEnd
      \vspace{-3pt}
    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Summary of Qualifications}
 \begin{itemize}[leftmargin=0.0in, label={}]
\resumeItemListStart
    \resumeItem{Proficient in Python, Go, SQL, NoSQL, Java, JavaScript, HTML, OAuth, operating systems, SDLC, data manipulation, Docker, Postman, GraphQL, Azure, XML, JWT, Linux, Kotlin, scripting, CI/CD automation, and REST API endpoints.}
    
    \resumeItem{Collaborated with student groups for sprint and PI planning, gathering requirements, demonstrating MVP solutions, and preparing financial and technical documentation, including diagrams and reports.}
    
    \resumeItem{Knowledgeable in database technologies, software development tools, programming languages, security technologies, Microsoft Office applications, Kubernetes, Tableau, React, Android Studio, Quality Assurance and User Assurance.}
    
    \resumeItem{Familiar with system design architecture, networking, frameworks, machine learning, NLP, Jupyter, business and information architectures, change management principles, and creating professional correspondence and presentations.}
\resumeItemListEnd
 \end{itemize}
%-------------------------------------------
\end{document}
